\textls[-0]{\thetitle}

### 2023-03-04 related-work.tex
One sentence about Intrinsically typed.

%DTC is as a source of inspiration for may approaches
%\cite{delaware2013,delaware2013b,schwaab2013modular,keuchel2013generic,forsta2020}.
The original DTC encoding requires type-level general recursion that
fails the strict positivity check imposed by proof assistants including Coq and Agda.
\citet{delaware2013} introduce \emph{meta-theory à la carte} (MTC):
it overcomes the problem by using Church encodings for
data types and using Mendler-style folds for evaluation,
though it requires \lsti{Set} impredicativity.
Feature composition is automated through heavy use of type classes.
The framework is implemented as a Coq library.
\citet{schwaab2013modular} adapt DTC to Agda by considering a restricted
class of functors that admit least fixed points.
\citet{keuchel2013generic} use datatype-generic programming techniques
for the underlying representation of type-level fixed points and
avoid \lsti{Set} impredicativity.\YZ{What can we say about Intrinsically-Typed Definitional Interpreters a La Carte?}\EDJreply{My understanding is,
 it is really an intrinsic typed version of MTC. It uses different set of tools (like containers (a la altenkirch, can be considered as an alternative of W-type) and stuff) but it is still a design pattern paper.
 But good news is, container is closer to Wtype(inductive type) than the endofunctor encoding (classic MTC approach).}
%\cite{vdr2022intrinsically}

@@

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
But even with the tool support, components (e.g., "substlem") of
individually developed feature extensions have to be composed separately
by invoking the tool.
%
%The approach does not seem to fully address the expression problem,
%as \citet{liwei2022} observe, in that further extending a composed
%mechanization causes (a small amount of) boilerplate code that glues definitions
%to be regenerated.

>>>>

%DTC is as a source of inspiration for may approaches
%\cite{delaware2013,delaware2013b,schwaab2013modular,keuchel2013generic,forsta2020}.
The original DTC encoding requires type-level general recursion that
fails the strict positivity check imposed by proof assistants including Coq and Agda.
\citet{delaware2013} introduce \emph{meta-theory à la carte} (MTC):
it overcomes the problem by using Church encodings for
data types and using Mendler-style folds for evaluation,
though it requires \lsti{Set} impredicativity.
Feature composition is automated through heavy use of type classes.
The framework is implemented as a Coq library.
\citet{schwaab2013modular} adapt DTC to Agda by considering a restricted
class of functors that admit least fixed points.
\citet{keuchel2013generic} use datatype-generic programming techniques
for the underlying representation of type-level fixed points and
avoid \lsti{Set} impredicativity.\YZ{What can we say about Intrinsically-Typed Definitional Interpreters a La Carte?}\EDJreply{My understanding is,
 it is really an intrinsic typed version of MTC. It uses different set of tools (like containers (a la altenkirch, can be considered as an alternative of W-type) and stuff) but it is still a design pattern paper.
 But good news is, container is closer to Wtype(inductive type) than the endofunctor encoding (classic MTC approach)}\EDJreply{I also add one sentence after Coq a la carte. You can also check... I will add bib later. Interestingly, Intrinsic type doesn't refer Coq a la carte.}
%\cite{vdr2022intrinsically}

@@

\citet{forsta2020} introduce \emph{Coq à la carte}.
It still follows DTC, but rather than embracing DTC's use of generic
fixed points, it considers specific instantiations instead.
The resulting mechanism appears more streamlined than prior \emph{à la
carte} approaches particularly for its extensive tool support for generating boilerplate code.
%
But even with the tool support, components (e.g., "substlem") of
individually developed feature extensions have to be composed separately
by invoking the tool. Alternatively, \citet{vdr2022intrinsically} uses 
containers and signature to mechanize intrinsically-typed target language. 
Combined with Agda's advanced unification mechanism, the authors get rid of 
a large number of boilerplate code. 
%
%The approach does not seem to fully address the expression problem,
%as \citet{liwei2022} observe, in that further extending a composed
%mechanization causes (a small amount of) boilerplate code that glues definitions
%to be regenerated.
